The \dealii{} Library, Version 9.3

### 2021-06-21 9.3/paper.tex

The major changes of this release are:
%
\begin{itemize}
  \item Experimental support for simplex and mixed meshes (see Section~\ref{subsec:simplex});
  \item Improved flexibility of the particle infrastructure (see Section~\ref{subsec:particles});
  \item Support for global-coarsening multigrid algorithms (see Section~\ref{subsec:mg});
  \item Advances in the matrix-free infrastructure  (see Section~\ref{subsec:mf});
  \item Usage of MPI-3.0 shared-memory features to reduce memory footprint  (see Section~\ref{subsec:sm});
  \item Improved support for evaluation and integration at arbitrary points (see Section~\ref{subsec:fepointvalues});
  \item Nine new tutorial programs and a new code gallery program (see Section~\ref{subsec:steps}).
\end{itemize}
%
In addition, we discuss the \candi{} installation program in Section~\ref{subsec:candi}.

@@

@@

\item \texttt{step-74} SIPG for the Poisson equation \todo[inline]{TODO}

>>>>

The major changes of this release are:
%
\begin{itemize}
  \item Experimental support for simplex and mixed meshes (see Section~\ref{subsec:simplex});
  \item Improved flexibility of the particle infrastructure (see Section~\ref{subsec:particles});
  \item Support for global-coarsening multigrid algorithms (see Section~\ref{subsec:mg});
  \item Advances in the matrix-free infrastructure  (see Section~\ref{subsec:mf});
  \item Usage of MPI-3.0 shared-memory features to reduce memory footprint  (see Section~\ref{subsec:sm});
  \item Improved support for evaluation and integration at arbitrary points (see Section~\ref{subsec:fepointvalues});
  \item Simplified implementation for face integrals (see Section~\ref{subsec:feinterfacevalues});
  \item Nine new tutorial programs and a new code gallery program (see Section~\ref{subsec:steps}).
\end{itemize}
%
In addition, we discuss the \candi{} installation program in Section~\ref{subsec:candi}.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Simplied implementation for face integrals}
\label{subsec:feinterfacevalues}
Discontinuous Galerkin (DG) methods require evaluations of averages and jumps accross cell faces, therefore we need to compute values of the shape functions and solutions from two adjacent cells. The \texttt{FEInterfaceValues} class is designed to provide an interface to directly obtain jumps and averages. When used with \texttt{MeshWorker::mesh\_loop()}, we can assemble face integrals in a uniform way independent of mesh types, which significantly simplifies the implementation.

Internally, this class provides an abstraction for two \texttt{FEFaceValues} objects (or \texttt{FESubfaceValues} when using adaptive refinement). The class introduces new interface degrees of freedom indices that are the union of the degrees of freedom indices of the two \texttt{FEFaceValues} objects. The interface degrees of freedom indices can be converted to the corresponding local degrees of freedom indices of the two cells using a helper function. Furthermore, this class supports vector-valued problems in a similar way as \texttt{FEFaceValues} does. We can easily obtain the corresponding scalar or vector values by providing an \texttt{FEValuesExtractors} object. Overall, this class is intended to be a low level replacement for \texttt{MeshWorker} and \texttt{LocalIntegrators}, and a higher level abstraction compared to assembling face terms manually.

Examples of \texttt{FEInterfaceValues} for scalar problems can be found in \texttt{step-12}, \texttt{step-47}, \texttt{step-50}, and the new tutorial \texttt{step-74}. Examples of vector-valued problems will be added in the future.

@@

\item \texttt{step-74} implements the symmetric interior penalty Galerkin 
(SIPG) method for Poisson's equation using the \texttt{FEInterfaceValues} class
in combination with \texttt{MeshWorker::mesh\_loop()}. This tutorial demonstrates a
simple and mesh-independent way to assemble face integrals.
